### 2019-02-26 sections/language.tex
explain difference between x and l
briefly explain internal vs. external

\label{sub:expressions}
The host language is a simply typed lambda calculus, extended with some basic types and \ML-style references.
We use references to represent shared data sources.
The grammar in \cref{fig:language-grammar} defines the syntax of the host language.
It has abstractions, applications, variables, and constants for booleans, integers and strings.
The symbol $\star$ stands for binary operators.
For the result of parallel tasks we need pairs.
Conditionals come in handy for defining guards.
%
References will be used to implement shared editors.
Our treatment of references closely follows the one by \citet{books/Pierce02TAPL}.
Creating a reference using the keyword $\Ref$ yields a location $l$.
Locations are not intended to be directly manipulated by the programmer.
The symbols ! and $:=$ stand for dereferencing and assignment.
The unit value will be used as the result of assignments.

\begin{figure}[h]
  \small
  \usemacro{G-Language-Compact}
  \caption{Language grammar} \label{fig:language-grammar}
\end{figure}
\fixme{Alejandro about l: different syntax from vars?}
\label{sub:notation}
We use double quotation marks to denote strings.
Integers are denoted by their decimal representation, and booleans are written $\True$ and $\False$.
We freely make use of the logic operators $\Not$, $\land$, and $\lor$, arithmetic operators $+$, $-$, $\times$, and the string append operator $\pp$.
Furthermore, we use standard comparison operations $<$, $\le$, $\equiv$, $\not\equiv$, $\ge$, and $>$.
The symbol $\star$ stands for any of those.
%
\label{sub:abbreviations}
The notation $e_1; e_2$ is an abbreviation for $(\lambda x:\Unit.\ e_2)\ e_1$, where $x$ is a fresh variable.
The notation $\Let x:\tau = e_1 \In e_2$ is an abbreviation for $(\lambda x:\tau.\ e_2)\ e_1$.

@@

\paragraph{Internal and external step $(t \Then e, t \Next e)$}\fixme{Alejandro: The naming is confusing to me}
\label{sub:steps}

Sequential composition has a task $t$ on the left and a continuation $e$ on the right.
The accompanying typing rules are \refrule{T-Then} and \refrule{T-Next}.
According to these rules, the left hand side must be a task $t : \Task \tau_1$, and the right hand side $e : \tau_1 \to \Task \tau_2$ must be a function that, given the task value of $t$, calculates the task with which to continue.

>>>>

\label{sub:expressions}
The host language is a simply typed lambda calculus, extended with some basic types and \ML-style references.
We use references to represent shared data sources.
The grammar in \cref{fig:language-grammar} defines the syntax of the host language.
It has abstractions, applications, variables, and constants for booleans, integers and strings.
The symbol $\star$ stands for binary operators.
For the result of parallel tasks we need pairs.
Conditionals come in handy for defining guards.
%
References will be used to implement shared editors.
Our treatment of references closely follows the one by \citet{books/Pierce02TAPL}.
Creating a reference using the keyword $\Ref$ yields a location $l$.
While $x$ denotes program variables, $l$ denotes store locations.
Locations are not intended to be directly manipulated by the programmer.
The symbols ! and $:=$ stand for dereferencing and assignment.
The unit value will be used as the result of assignments.

\begin{figure}[h]
  \small
  \usemacro{G-Language-Compact}
  \caption{Language grammar} \label{fig:language-grammar}
\end{figure}
\label{sub:notation}
We use double quotation marks to denote strings.
Integers are denoted by their decimal representation, and booleans are written $\True$ and $\False$.
We freely make use of the logic operators $\Not$, $\land$, and $\lor$, arithmetic operators $+$, $-$, $\times$, and the string append operator $\pp$.
Furthermore, we use standard comparison operations $<$, $\le$, $\equiv$, $\not\equiv$, $\ge$, and $>$.
The symbol $\star$ stands for any of those.
%
\label{sub:abbreviations}
The notation $e_1; e_2$ is an abbreviation for $(\lambda x:\Unit.\ e_2)\ e_1$, where $x$ is a fresh variable.
The notation $\Let x:\tau = e_1 \In e_2$ is an abbreviation for $(\lambda x:\tau.\ e_2)\ e_1$.

@@

\paragraph{Internal and external step $(t \Then e, t \Next e)$}
\label{sub:steps}

Sequential composition has a task $t$ on the left and a continuation $e$ on the right.
External steps ($\Next$) must be triggered by the user, while internal steps ($\Then$) are taken automatically.
The accompanying typing rules are \refrule{T-Then} and \refrule{T-Next}.
According to these rules, the left hand side must be a task $t : \Task \tau_1$, and the right hand side $e : \tau_1 \to \Task \tau_2$ must be a function that, given the task value of $t$, calculates the task with which to continue.
